---
title: "Clustering
author: "William Taylor Bickelmann"
date: 2017-11-09
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Clustering is the technique of dividing the population into groups based on similar characteristics. Useful when there are too many variables that could mark similarities; Youre not sure which category is going to yield the best results in categorization

Hard clustering has a binary possibility when classifying a data point into a cluster; it is or it isn't. 

Soft clustering involves calculating a likelihood that a data point is in one of the clusters

There are various methods of clustering but the most common is K-means clustering; which maximizes the distance between clusters and computes cluster similarity based on distance (usually Euclidean).

K-Means represents the number of clusters in which we want our data to divide into. The basic restriction for K-Means algorithm is that your data should be continuous in nature. It won't work if data is categorical in nature.

K-means is iterative- that is to say it repeats the task of maximizing the distance between clusters until process is complete. 
It computes cluster centroids - then assigns all the data points close to it to that cluster then repeats the process
##Step 1: Data Loading and Cleaning
```{r}
library(NbClust)
iris<-data.frame(iris3)
iris<-read.csv("C:/Users/William/Documents/Datasets/Iris.csv")
iris1<-read.csv("C:/Users/William/Documents/Datasets/Iris.csv")
head(iris)
iris<-iris[,c(-1,-6)]
head(iris)
```



##Step 2: Data Normalization
```{r}
iris<-scale(iris)
kmeans.iris<-kmeans(iris,3,nstart = 20)
summary(kmeans.iris)
kmeans.iris$centers
```
This

```{r}
table(kmeans.iris$cluster, iris1$Species)

```

